\documentclass[defaultstyle,11pt]{thesis}

\usepackage{amssymb}		% to get all AMS symbols
\usepackage{graphicx}		% to insert figures
\usepackage{hyperref}		% PDF hyperreferences??
\usepackage{tikz}
\usetikzlibrary{chains}
\usepackage{outlines}
\renewcommand*{\familydefault}{\sfdefault}
\usepackage{pgfplots}
\pgfplotsset{width=10cm,compat=1.9}
\usepgfplotslibrary{external}
\tikzexternalize

%%%%%%%%%%%%   All the preamble material:   %%%%%%%%%%%%

\title{Authenticating Logs with Blockchain in Neutral Vehicles}

\author{Anya}{Owsenek}
\otherdegrees{}

\degree{Bachelor of Science in Computer Science}		%  #1 {long descr.}
	{B.S., Computer Science}		%  #2 {short descr.}

\dept{Department of}			%  #1 {designation}
	{Computer Science}		%  #2 {name}

\advisor{Professor}				%  #1 {title}
	{Dan Massey}			%  #2 {name}

\reader{Professor Jim Curry}		%  2nd person to sign thesis
\readerThree{Professor Qin (Christine) Lv }		%  3rd person to sign thesis

\abstract{  \OnePageChapter	% because it is very short

	\indent 
        Modern computer systems rely on logging events to keep track of actions that have taken place on a system. However, these logs are not secured, which means that if an attacker compromises a system, they can, and will, modify those logs to remove any traces of their presence. The need for verifying vehicular logs stems from the lack of methods to ensure drivers are following the regulations of their profession.  \textbf{This thesis aims to use blockchain technology to secure vehicular logs through tamper detection.} Initial efforts to mitigate tampering will use a blockchain of log contents, and the immutable-log software proposed will help with driver accountability and regulation enforcement. Detection of log tampering will take a multidisciplinary approach that leverages the benefits of a blockchain-reinforced log and the inter-dependencies of the data inherent to logs generated by vehicles. There are currently no effective tamper-resistant approaches to protecting log data.
	}

\dedication[Dedication]{	% NEVER use \OnePageChapter here.
	To all of the fluffy kitties.
	}

\acknowledgements{	\OnePageChapter	% *MUST* BE ONLY ONE PAGE!
	Here's where you acknowledge folks who helped.
	But keep it short, i.e., no more than one page,
	as required by the Grad School Specifications.
	}

% \IRBprotocol{E927F29.001X}	% optional!

\ToCisShort	% use this only for 1-page Table of Contents

\LoFisShort	% use this only for 1-page Table of Figures
% \emptyLoF	% use this if there is no List of Figures

\LoTisShort	% use this only for 1-page Table of Tables
% \emptyLoT	% use this if there is no List of Tables

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\input relatedWork.tex
\input ProblemStatement.tex
\input threatModel.tex
\input implementation.tex
\input attacks.tex
%\input data.tex
\input conclusion.tex
%\input software.py

%%%%%%%%%   then the Bibliography, if any   %%%%%%%%%
\bibliographystyle{plain} % or "siam", or "alpha", etc.
\nocite{*}		% list all refs in database, cited or not
\bibliography{refs}		% Bib database in "refs.bib"

%%%%%%%%%   then the Appendices, if any   %%%%%%%%%
%\appendix
%\input appendixA.tex
%\input appendixB.tex


\end{document}

